---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---
M.van Heezik

## Loading and preprocessing the data
```{r}
data<-read.csv("./activity.csv", na="NA")
```

## What is mean total number of steps taken per day?
```{r}
library(dplyr)
data.summ <-summarise_each(group_by(data, date ), funs(sum))
hist(data.summ$steps,breaks=20,main="Histogram of Total steps per day")

#mean(data.summ$steps, na.rm = TRUE )
#median(data.summ$steps, na.rm = TRUE )

```
The mean total number of steps taken per day is: `r mean(data.summ$steps, na.rm = TRUE )`  
The median total number of steps taken per day is: `r median(data.summ$steps, na.rm = TRUE )`

## What is the average daily activity pattern?
```{r}
data.summ2 <-summarise_each(group_by(data[!is.na(data$steps),], interval ), funs(mean))
plot(x=data.summ2$interval, y=data.summ2$steps, type="l",main="Average steps per interval",
     xlab="interval", ylab="average steps")
data.max<-data.summ2[which.max(data.summ2$steps),]

```

The maximum average steps is `r data.max[1,]$steps` and found at interval `r data.max[1,]$interval`


## Imputing missing values
```{r}
data.corrected <- merge(data[is.na(data$steps),c("interval","date")],data.summ[,c("interval","steps")],by="interval")
data.combi<-rbind(data.corrected, data[!is.na(data$steps),])

data.summ3 <-summarise_each(group_by(data.combi, date ), funs(sum))
hist(data.summ3$steps,breaks=20,main="Histogram of Total steps per day (imputed data)")


```

There are `r nrow(data[is.na(data$steps),])` missing values in the dataset  
The imputed mean total number of steps taken per day is: `r mean(data.summ3$steps, na.rm = TRUE )`  
The imputed median total number of steps taken per day is: `r median(data.summ3$steps, na.rm = TRUE )`

The difference in mean total number of steps taken per day is: `r mean(data.summ3$steps, na.rm = TRUE ) - mean(data.summ$steps, na.rm = TRUE )`  
The imputed median total number of steps taken per day is: `r median(data.summ3$steps, na.rm = TRUE )  - median(data.summ$steps, na.rm = TRUE )`  

There is negligible impact of imputing missing values

## Are there differences in activity patterns between weekdays and weekends?
```{r}
library(ggplot2)

data.combi$day<-as.Date(data.combi$date,format = "%Y-%m-%d")
data.combi$weekday<-ifelse(weekdays(data.combi$day) %in% c("zondag","zaterdag"),"Weekend", "Weekday")

data.summ4 <-summarise_each(group_by(data.combi,  weekday, interval ), funs(mean))

qplot(x=data.summ4$interval, y=data.summ4$steps, data=data.summ4, main="Average steps per interval",
     xlab="interval", ylab="average steps", facets=weekday~., geom="line")
```
