---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---
M.van Heezik

## Loading and preprocessing the data
```{r}
data<-read.csv("./activity.csv", na="NA")
```

## What is mean total number of steps taken per day?
```{r}
library(dplyr)
data.summ <-summarise_each(group_by(data, date ), funs(sum))
hist(data.summ$steps,breaks=20,main="Histogram of Total steps per day")

#mean(data.summ$steps, na.rm = TRUE )
#median(data.summ$steps, na.rm = TRUE )

```
The mean total number of steps taken per day is: `r mean(data.summ$steps, na.rm = TRUE )`  
The median total number of steps taken per day is: `r median(data.summ$steps, na.rm = TRUE )`

## What is the average daily activity pattern?
```{r}
data.summ <-summarise_each(group_by(data[!is.na(data$steps),], interval ), funs(mean))
plot(x=data.summ$interval, y=data.summ$steps, type="l",main="Average steps per interval",
     xlab="interval", ylab="average steps")
data.max<-data.summ[which.max(data.summ$steps),]

```

The maximum average steps is `r data.max[1,]$steps` and found at interval `r data.max[1,]$interval`


## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
